Bioverse: Origins of Life

### 2023-09-16 src/tex/ms.tex
distinguish between injected signal and hypothesis

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on a planet with a minimum past UV flux.
Here, we focus on the prebiotically interesting \SIrange{200}{280}{\nano\meter} range CITE and the quiescent stellar flux.  %~\citep{RanjanSasselov2016}.
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received UV radiation in this wavelength range that exceeded a minimum NUV flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for $\geq \SI{100}{\mega\year}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
We then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \, \mathrm{for} \, \Delta t \geq \SI{100}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\section{Exoplanet survey simulations}
\todo[inline]{biomarkers: Focus on molecular Oxygen? Excess Methane? \citep[e.g.,][]{Seeburger2023}}
A commonly discussed biomarker is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
While not the only atmospheric species discussed as a signature for planetary life CITE, we focused on O$_2$ as a representative biomarker for our spectroscopic survey simulations.

>>>>

\subsection{H3: Life only originates on planets with particular UV irradiance}
Our third theoretical experiment is to test the UV irradiance requirement (Sect.~\ref{sec:predictions:uv}) by relating the occurrence of life on a planet with a minimum past UV flux.
Here, we focus on the prebiotically interesting \SIrange{200}{280}{\nano\meter} range CITE and the quiescent stellar flux.  %~\citep{RanjanSasselov2016}.
Our concrete hypothesis shall be that life only occurs on planets that at some point in their history have received UV radiation in this wavelength range that exceeded a minimum NUV flux $F_\mathrm{NUV, min}$.
We further require this flux to have lasted for $\geq \SI{100}{\mega\year}$ to allow for a sufficient ``origins timescale''~\citep{Rimmer2023}.
We assign the development of life to a fraction $f_\mathrm{life}$ of all temperate planets fulfilling these requirements.
For a population-level hypothesis, we then have
\begin{equation}\label{eq:hypothesis-uv}
    H_{3} = f_\mathrm{life} (\theta, F_\mathrm{NUV}) =
        \begin{cases}
            0 , & F_\mathrm{NUV} < F_\mathrm{NUV, min}\\
            f_\mathrm{life}, & F_\mathrm{NUV} \geq F_\mathrm{NUV, min} \, \mathrm{for} \, \Delta t \geq \SI{100}{\mega\year}
        \end{cases}
\end{equation}
and the corresponding null hypothesis
%\begin{equation}
$H_{3, null} = f_\mathrm{life} (\theta),$
%\end{equation}
i.e., no correlation with UV flux.

@@

\section{Exoplanet survey simulations}
\todo[inline]{biomarkers: Focus on molecular Oxygen? Excess Methane? \citep[e.g.,][]{Seeburger2023}}
% detecting methanogenic life: Sandora2020, Wang2018,
A commonly discussed biomarker is molecular Oxygen (O$_2$), which on Earth emerged as a byproduct of photosynthesis during the Proterozoic era.
While not the only atmospheric species discussed as a signature for planetary life CITE, we focused on O$_2$ as a representative biomarker for our spectroscopic survey simulations.
